The problem and promise of scale in multilayer networks

### 2020-01-22 paper/manuscript.Rmd
edit P1 intro

## Introduction
Our understandings of ecological pattern and process are directly linked to the scale at which they are observed (Levin 1992; Allen et al. 2015). Animals and landscapes are influenced across scales by higher level processes, such as climate and productivity (Field et al. 2009) and lower level processes, such as species interactions and resource availability (Legendre 1993; Chave 2013). The effect of scale in ecology has been explored through species distributions (Elith et al. 2009) habitat selection (Mayor et al. 2007) and food webs (Sugihara et al. 1989). Scale can be considered for all types of measured quantities including spatial and temporal variables, as well as behavioural variables, including sociality.

>>>>

## Introduction
Our understandings of ecological pattern and process are directly linked to the scale at which they are observed (Levin 1992; Allen et al. 2015). Animals and landscapes are influenced across scales processes as global as climate and productivity (Field et al. 2009), and species-specific as trophic interactions and resource availability (Legendre 1993; Chave 2013). The effect of scale in ecology has been explored through species distribution modelling (Elith et al. 2009), habitat selection (Mayor et al. 2007), and food webs (Sugihara et al. 1989). Scale can be considered throughout ecology, including animal behaviour and the social environment that animals experience.
